<span style="color:red;">*ANTs*</span><br> <small>_power tools for neuroimaging_</small>

### 2014-10-30 ants2015_GE.Rmd
ENH:  Final changes.

##

![](./figures/brian_and_nick.png)

>>>>

## Founding developers

<div align="center"><img width="1800" src="./figures/brian_and_nick.png" frameborder="0"></img></div>

## Long term collaborators

![](./figures/antscollab.jpg)

## _ANTs_:  General purpose library for multivariate image registration, segmentation & statistical analysis tools

* 170,000+ lines of C++, 6$+$ years of work, 15+ collaborators.

* Generic mathematical methods that are tunable for
application specific domains:  no-free lunch

* Deep testing on multiple platforms ... osx, linux, windows.

* Several "wins" in public knock-abouts ( [Klein 2009](http://www.ncbi.nlm.nih.gov/pubmed/19195496), [Murphy 2011](http://www.ncbi.nlm.nih.gov/pubmed/21632295), [SATA 2012 and 2013](http://www.ncbi.nlm.nih.gov/pmc/articles/PMC3837555/), [BRATS 2013](http://martinos.org/qtim/miccai2013/proc_brats_2013.pdf), others )

```
    An algorithm must use prior knowledge about a problem
    to do well on that problem
```

### 2014-10-30 ants2015build.Rmd
ENH:  Final changes.

![](./figures/brian_and_nick.png)

>>>>

## Founding developers

<div align="center"><img width="1800" src="./figures/brian_and_nick.png" frameborder="0"></img></div>

## Long term collaborators

![](./figures/antscollab.jpg)

## _ANTs_:  General purpose library for multivariate image registration, segmentation & statistical analysis tools

* 170,000+ lines of C++, 6$+$ years of work, 15+ collaborators.

* Generic mathematical methods that are tunable for
application specific domains:  no-free lunch

* Deep testing on multiple platforms ... osx, linux, windows.

* Several "wins" in public knock-abouts ( [Klein 2009](http://www.ncbi.nlm.nih.gov/pubmed/19195496), [Murphy 2011](http://www.ncbi.nlm.nih.gov/pubmed/21632295), [SATA 2012 and 2013](http://www.ncbi.nlm.nih.gov/pmc/articles/PMC3837555/), [BRATS 2013](http://martinos.org/qtim/miccai2013/proc_brats_2013.pdf), others )

```
    An algorithm must use prior knowledge about a problem
    to do well on that problem
```
